Scheeper's Meager-NWD Game and the Menger Game

### 2014-12-16 phd/dissertation/chapter2.tex
introductory chapter
make changes suggested by G

\chapter{Introduction}

The goal of this paper is to explore the applications of limited information
strategies in existing topological games.

@@

Games may be modeled mathematically in various ways,
but we will find it convenient to think of them in terms defined by
Gale and Stewart. \cite{MR0054922}

@@

\begin{game}
  Let $\bakergame{X}$ denote a game with players $\pl A$ and $\pl B$,
  defined for each subset $A\subset \mathbb{R}$.
  In round $0$, $\pl A$ chooses a number $a_0$, followed by $\pl B$ choosing
  a number $b_0$ such that $a_0<b_0$.
  In round $n+1$, $\pl A$ chooses a number $a_{n+1}$ such that
  $a_n<a_{n+1}<b_n$, followed by $\pl B$ choosing a number $b_{n+1}$ such that
  $a_{n+1}<b_{n+1}<b_n$.

  $\pl A$ wins the game if the sequence $\<a_n:n<\omega\>$ limits to a
  point in $X$, and $\pl B$ wins otherwise.
\end{game}

@@

\begin{proof}
  Adapted from \cite{noMRbaker}.
  Let $X=\{x_0,x_1,\dots\}$. Let $i(a,b)$ be the least integer such that
  $a<x_{i(x,y)}<b$, if it exists. We define a strategy $\sigma$ for $\pl B$
  such that:
  \begin{itemize}
    \item $\sigma(\<a_0\>)=x_{i(a_0,\infty)}$.
          If $i(a_0,\infty)$ does not exist, then the choice of $\sigma(\<a_0\>)$
          is arbitary, say, $a_0+1$.
    \item $\sigma(\<a_0,...,a_{n+1}\>)=x_{i(a_{n+1},b_n)}$, where
          $b_n=\sigma(\<a_0,\dots,a_n\>)$.
          If $i(a_{n+1},b_n)$ does not exist, then the choice of
          $\sigma(\<a_0,...,a_{n+1}\>)$ is arbitrary, say,
          $
            \sigma(\<a_0,...,a_{n+1}\>)
              =
            \frac{a_{n+1}+b_n}{2}
          $.
  \end{itemize}

  Observe that $\sigma$ is a legal strategy according to the rules of the game
  since $a_0<\sigma(\<a_0\>)$ and $a_{n+1}<\sigma(\<a_0,\dots,a_{n+1}\>)<b_n$.
  We claim this is a winning strategy for $\pl B$. Let $a=\<a_0,a_1,\dots\>$
  be a legal attack by $\pl A$ against $\sigma$: we will show that the
  resulting playthrough is a victory for $\pl B$, that is,
  $\lim_{n\to\infty} a_n\not\in X$. Let $b_n=\sigma(\<a_0,\dots,a_n\>)$.
  Note that
    \[
      a_0<a_1<\dots<\lim_{n\to\infty}a_n<\dots<b_1<b_0
    \]

  If $i(a_0,\infty)$ does not exist, then $a_0$ is greater than every element
  of $X$, and thus
  $\lim_{n\to\infty} a_n \not\in X$. A similar argument follows if some
  $i(a_{n+1},b_n)$ does not exist.

  Otherwise,
    \[
      i(a_0,\infty)<i(a_1,b_0)<i(a_2,b_1)<\dots
    \]
  and for each $i<\omega$, one of the following must hold.
    \begin{itemize}
      \item $i<i(a_0,\infty)$. Then $x_i\leq a_0<\lim_{n\to\infty}a_n$.
      \item $i = i(a_0,\infty)$. Then $x_i=b_0>\lim_{n\to\infty}a_n$.
      \item $i(a_0,\infty)<i<i(a_1,b_0)$.
            Then $x_i\leq a_1<\lim_{n\to\infty}a_n$ or
            $x_i\geq b_0>\lim_{n\to\infty}a_n$.
      \item $i = i(a_{n+1},b_n)$ for some $n<\omega$.
            Then $x_i=b_{n+1}>\lim_{n\to\infty}a_n$.
      \item $i(a_{n+1},b_n)<i<i(a_{n+2},b_{n+1})$ for some $n<\omega$.
            Then $x_i\leq a_{n+2}<\lim_{n\to\infty}a_n$ or
            $x_i\geq b_{n+1}>\lim_{n\to\infty}a_n$.
    \end{itemize}
  In any case, $x_i\not=\lim_{n\to\infty}a_n$, and thus
  $\lim_{n\to\infty}a_n\not\in X$.
\end{proof}

More informally, $\pl B$ can force a win by enumerating the countable set
$X$ and playing every legal choice by the end of the game.
This yields a classical result.

>>>>

\chapter{Definitions and Examples}

This chapter outlines the set-theoretic and game-theoretic preliminaries
required for this paper.

\section{Set Theory}

In general, all required set-theoretic concepts are taken from Kunen's
text \cite{MR597342}.

\begin{defn}
  Define \term{ordinals} and \term{cardinals} as in Kunen's text.
  In particular, $0=\emptyset$, $\omega=\{0,1,2,\dots\}$,
  $\omega_1$ is the smallest uncountable ordinal, and
  $\alpha+1=\alpha\cup\{\alpha\}$. The order on ordinals and cardinals
  is given by $\alpha<\beta$ if and only if $\alpha\in\beta$.
\end{defn}

\begin{defn}
  Let $R^D$ denote the set of functions from $D$ to $R$. For an ordinal
  $\alpha$, $R^{<\alpha}=\bigcup_{\beta<\alpha}R^\beta$ and
  $R^{\leq\alpha}=\bigcup_{\beta\leq\alpha}R^\beta$.
\end{defn}

\begin{defn}
  A \term{sequence} is a function $f\in A^\omega$, denoted
  $f=\<f(0),f(1),\dots\>$.
  A \term{finite sequence} is a function
  $t\in A^{<\omega}$, denoted $t=\<t(0),\dots,t(|t|-1)\>$.
\end{defn}

Ordered pairs, triples, etc. are considered to be finite sequences.

\begin{defn}
  For $s,t\in A^{<\omega}$, let $s\concat t\in A^{<\omega}$ be the
  \term{concatenation} of $s$ and $t$, so that $(s\concat t)(i)=s(i)$
  for $i<|s|$, and $(s\concat t)(i+|s|)=t(i)$ for $i<|t|$.
\end{defn}

\begin{defn}
  For $f:D\to R$ and $A\subseteq D$, let $f\rest A : A\to R$ be the
  \term{restriction} of $f$ to $A$.
\end{defn}

@@

Games may be modeled mathematically in various ways,
but we will find it convenient to think of them in terms defined by
Gale and Stewart \cite{MR0054922}.

@@

\begin{game}
  Let $\bakergame{X}$ denote a game with players $\pl A$ and $\pl B$,
  defined for each subset $X\subset \mathbb{R}$.
  In round $0$, $\pl A$ chooses a number $a_0$, followed by $\pl B$ choosing
  a number $b_0$ such that $a_0<b_0$.
  In round $n+1$, $\pl A$ chooses a number $a_{n+1}$ such that
  $a_n<a_{n+1}<b_n$, followed by $\pl B$ choosing a number $b_{n+1}$ such that
  $a_{n+1}<b_{n+1}<b_n$.

  $\pl A$ wins the game if the sequence $\<a_n:n<\omega\>$ converges to a
  point in $X$, and $\pl B$ wins otherwise.
\end{game}

@@

\begin{proof}
  Adapted from \cite{noMRbaker}.
  Let $X=\{x_i:i<\omega\}$. Let $i(a,b)$ be the least integer such that
  $a<x_{i(x,y)}<b$, if it exists. We define a strategy $\sigma$ for $\pl B$
  such that:
  \begin{itemize}
    \item If $i(a_0,\infty)$ exists, $\sigma(\<a_0\>)=x_{i(a_0,\infty)}$.
    \item Let $b_n=\sigma(\<a_0,\dots,a_n\>)$
          If $i(a_{n+1},b_n)$ exists,
          $\sigma(\<a_0,...,a_{n+1}\>)=x_{i(a_{n+1},b_n)}$.
    \item Otherwise, the choice of $\sigma(t)$ may be any legal move.
  \end{itemize}

  Observe that $\sigma$ is a legal strategy according to the rules of the game
  since $a_0<\sigma(\<a_0\>)$ and $a_{n+1}<\sigma(\<a_0,\dots,a_{n+1}\>)<b_n$.
  Note every $x_i$
  was either chosen by $\pl B$ during a round, or it was illegal to choose.
  In either case, there exist $a_n,b_n$ with $x_i\not\in(a_n,b_n)$, so
  $\lim_{n\to\infty}a_n\not\in X$ and thus $\sigma$ is a winning strategy.
\end{proof}

This yields the classical result from undergraduate set theory.

### 2014-12-16 phd/dissertation/chapter3.tex
overall cleanup
all theorems/definitions within sections for numbering
make changes suggested by G

We begin by investigating a game due to Gary Gruenhage.

@@

\begin{thm}
  $\pl O \not\markwin \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
\end{thm}

@@

\begin{thm}
  $\pl O \not\kmarkwin{k} \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
\end{thm}

@@

However, knowledge of the round number is critical.

\begin{thm}
  $O\not\ktactwin{k}\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a $k$-tactic for $\pl O$ in
  $\gruClusGameHard{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_1
          :
        s\in\alpha^{\leq k}
          \Rightarrow
        \oneptcomp\omega_1\setminus\sigma(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. Let $a_\sigma:\omega_1\to C_\sigma$ be an order
  isomorphism.

@@

\begin{thm}
  $O\not\kmarkwin{k}\gruClusGameHard{\oneptcomp\omega_2}{\infty}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a $k$-mark for $\pl O$ in
  $\gruClusGame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_2
          :
        s\in\alpha^{<\omega}
          \Rightarrow
        \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
        \subset \alpha
      \}
    \]
  is closed and unbounded. (Recall that $\mu_k$ is the
  $k$-Markov fog-of-war which turns perfect information into the last $k$
  moves and the round number.) Let $a_\sigma:\omega_2\to C_\sigma$ be
  an order isomorphism.

@@

\begin{defn}
  Let $\Sigma_{y} \prod_{\alpha<\kappa}X_\alpha$ be a \term{sigma-product} of
  $X$ with dimension $\kappa$ for each $y\in \prod_{\alpha<\kappa}X_\alpha$,
  the subset of the usual Tychonoff product space $\prod_{\alpha<\kappa}X_\alpha$
  such that $x\in \Sigma_y \prod_{\alpha<\kappa}X_\alpha$
  if and only if $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.

  Unless otherwise specified, we assume $0\in X_\alpha$ for all $\alpha<\kappa$
  and $y=\vec 0$, and write $\Sigma \prod_{\alpha<\kappa}X_\alpha$.
\end{defn}

\begin{prop}
  $\oneptcomp\kappa$ is homeomorphic to the space
  \[
    \{
    x\in \Sigma 2^\kappa
      :
    x(\alpha)=0 \text{ for all but one } \alpha<\kappa
    \}
  \]
\end{prop}

\begin{proof}
  Map $\alpha<\kappa$ to $x_\alpha$ such that
  \[
    x_\alpha(\beta) =
    \left\{
      \begin{array}{ll}
        0 & \beta\not=\alpha \\
        1 & \beta=\alpha
      \end{array}
    \right.
  \]
  and map $\infty$ to the zero vector $\vec0$.
\end{proof}

\begin{cor}
  $\pl O\not\ktactwin{k}\gruClusGameHard{\SigmaProdR{\omega_1}}{\vec0}$,
  $\pl O\not\kmarkwin{k}\gruConGameHard{\SigmaProdR{\omega_1}}{\vec0}$, and
  $\pl O\not\kmarkwin{k}\gruClusGameHard{\SigmaProdR{\omega_2}}{\vec0}$.
\end{cor}

@@

\begin{defn}
  For a game $G=\<M,W\>$ and \term{coding strategy} or \term{code}
  $\sigma:M^2\to M$, the \term{$\sigma$-coding fog-of-war}
  $\gamma_\sigma: M^{<\omega}\to M^{\leq2}$ is the function defined such that
    \[
      \gamma_\sigma(\emptyset) = \emptyset
    \]
  and
    \[
      \gamma_\sigma(s\concat\<x\>) = \<\sigma\circ\gamma_\sigma(s),x\>
    \]

>>>>

We begin by investigating a game due to Gary Gruenhage, introduced in
his doctoral dissertation to solve a problem due to Phil Zenor.

\section{Definitions}

@@

\begin{thm}
  $\pl O \notmarkwin \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
\end{thm}

@@

\begin{thm}
  $\pl O \notkmarkwin{k} \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
\end{thm}

@@

However, knowledge of the round number is critical. First recall the
following ``closing-up lemma'' (see \cite{MR597342}):

\begin{lem}
  For any function $f:\omega_1^{<\omega}\to\omega_1$, the following set is closed
  and unbounded in $\omega_1$:
    \[
      \{
        \alpha<\omega_1
      :
        s\in\alpha^{<\omega} \Rightarrow f(s)\subseteq\alpha
      \}
    \]
\end{lem}

\begin{thm}
  $\pl O\notktactwin{k}\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a $k$-tactic for $\pl O$ in
  $\gruClusGameHard{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_1
          :
        s\in\alpha^{\leq k}
          \Rightarrow
        \oneptcomp\omega_1\setminus\sigma(s)
        \subseteq \alpha
      \}
    \]
  is closed and unbounded. Let $a_\sigma:\omega_1\to C_\sigma$ be an order
  isomorphism.

@@

\begin{thm}
  $\pl O\notkmarkwin{k}\gruClusGameHard{\oneptcomp\omega_2}{\infty}$.
\end{thm}

\begin{proof}
  Let $\sigma$ be a $k$-mark for $\pl O$ in
  $\gruClusGame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
    \[
      C_\sigma
        =
      \{
        \alpha<\omega_2
          :
        s\in\alpha^{<\omega}
          \Rightarrow
        \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
        \subseteq \alpha
      \}
    \]
  is closed and unbounded. (Recall that $\mu_k$ is the
  $k$-Markov fog-of-war which turns perfect information into the last $k$
  moves and the round number.) Let $a_\sigma:\omega_2\to C_\sigma$ be
  an order isomorphism.

@@

\begin{defn}
  Let
    \[
      \sum_{\alpha<\kappa}^y X_\alpha
        =
      \left\{
        x \in \prod_{\alpha<\kappa} X_\alpha
         :
        |\{x(\alpha)\not=y(\alpha):\alpha<\kappa\}|\leq\omega
      \right\}
    \]
  denote the \term{sigma-product}
  of $\{X_\alpha:\alpha<\kappa\}$ with base point
  $y\in \prod_{\alpha<\kappa}X_\alpha$. The topology on this space
  is given by the subspace topology.

  Note also the following syntactic sugar:
  $\sum_{\alpha<\kappa}X_\alpha=\sum_{\alpha<\kappa}^{\vec 0}X_\alpha$,
  $\sum^{y} X^\kappa = \sum_{\alpha<\kappa}^{y} X$, and
  $\sum X^\kappa = \sum_{\alpha<\kappa}^{\vec 0} X$.
\end{defn}

\begin{prop}
  $\oneptcomp\kappa$ is homeomorphic to the space
  \[
    \left\{
    x\in \sum 2^\kappa
      :
    |\{\alpha<\kappa:x(\alpha)=1\}|\leq 1
    \right\}
  \]
\end{prop}

\begin{proof}
  Map $\alpha<\kappa$ to $x_\alpha$ such that
  \[
    x_\alpha(\beta) =
    \left\{
      \begin{array}{l@{\,:\,}l}
        0 & \beta\not=\alpha \\
        1 & \beta=\alpha
      \end{array}
    \right.
  \]
  and map $\infty$ to the zero vector $\vec0$.
\end{proof}

\begin{cor}
  $\pl O\notktactwin{k}\gruClusGameHard{\SigmaProdR{\omega_1}}{\vec0}$,
  $\pl O\notkmarkwin{k}\gruConGameHard{\SigmaProdR{\omega_1}}{\vec0}$, and
  $\pl O\notkmarkwin{k}\gruClusGameHard{\SigmaProdR{\omega_2}}{\vec0}$.
\end{cor}

@@

\begin{defn}
  For a game $G=\<M,W\>$ and \term{coding strategy} or \term{code}
  $\sigma:M^{\leq2}\to M$, the \term{$\sigma$-coding fog-of-war}
  $\gamma_\sigma: M^{<\omega}\to M^{\leq2}$ is the function defined such that
    \[
      \gamma_\sigma(\emptyset) = \emptyset
    \]
  and
    \[
      \gamma_\sigma(s\concat\<x\>) = \<\sigma\circ\gamma_\sigma(s),x\>
    \]

### 2014-12-16 phd/dissertation/chapter5.tex
make changes suggested by G

The reason why $\gruConGame{\oneptcomp X}{\infty}$ and $\gruKPGame{X}$ are
not completely equivalent is due to the fact that $\pl P$ may hide information
from $\pl O$ by playing $\infty$. These moves cannot trivially be ignored
using a $k$-limited information strategy for $k\geq 2$, since $\pl P$ may
ensure that only one ``useful'' move may be seen by $\pl K$ at a time by playing
$k$ $\infty$s between each non-$\infty$.

@@

@@

@@

A similar game may be considered by allowing the second player to choose
compact sets rather than points, which also provided in \cite{MR858337}
a game-theoretic characterization of a covering property for locally compact
spaces.

\begin{game}
  Let $\gruKLGame{X}$ denote the \term{Gruenhage compact/compact game}
  with players $\pl K$, $\pl L$. This game proceeds analogously to
  $\gruKPGame{X}$, except the second player $\pl L$ chooses comapct sets $L_n$
  missing $\bigcup_{m\leq n}K_n$,
  and $\pl K$ wins if the collection $\{L_n:n<\omega\}$ is locally finite.
\end{game}

@@

@@

\begin{defn}
  A space $X$ is \textbf{hemicompact} if there exist compact sets $K_n$ for
  $n<\omega$ such that every compact set in $X$ is a subset of some $K_n$.
\end{defn}

@@

\begin{proof}
  Let $\sigma$ be a winning predetermined strategy for $\pl K$ in
  $\gruKPGame{X}$. If $C\in \mc K(X)$ is compact, then for each $x\in C$ let
  $U_x$ be an open neighborhood of $x$ which intersects finitely many
  $\sigma(n)$. Thus there exists an open neighborhood of $C$ which intersects
  finitely many $\sigma(n)$.
\end{proof}

@@

It is not possible to prove that $\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$
for arbitrary free ultrafilters in $ZFC$.

@@

\begin{defn}
  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct
  clopen sets, along with an uncountable subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\pmb X$ is given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $B_{\alpha,n}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
  $m<\omega$.
\end{defn}

@@

\begin{lem}
  Then $K_F$, $K_F'$, $L_m$ are compact in $\pmb X$.
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lem}

@@

  Then consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
  Then if $\pmb p(n)=\<x,s\>$ with $\alpha = \alpha_{x,N}$ for some $N<\omega$,
  then $\pmb p(m)\not\in B_{\alpha,0}$ for $\max(n,N)<m<\omega$.
  Or, if $\pmb p(n)=c_\alpha$, then
  $\pmb p(m)\not\in B_{\alpha,0}$ for $n<m<\omega$.
  Otherwise, $\pmb p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
  In any case, $B_{\alpha,0}$ is a neighborhood of $\pmb x$ which contains finitely
  many $\pmb p(n)$. Therefore, $\sigma$ is a winning strategy.
\end{proof}

@@

\begin{proof}
  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
  compact; one such space was constructed in \cite{Marciszewski1991291}
  and let $X=Y^2$.
  Then by characterizations of Corson and Eberlien compacts found in
  \cite{MR752278},
  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
  clopen cover of $X$ which is not $\sigma$-point-finite.
\end{proof}

\begin{cor}
  There exists a space $X$ such that $\pl K\win\gruKPGame{X}$ but
  $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
\end{cor}

So the following question remains open:

\begin{ques}
  Does $\pl K\ktactwin{k+1}\gruKPGame{X}$ imply
  $\pl K\tactwin\gruKPGame{X}$ always? What about for Markov strategies?
\end{ques}

>>>>

The reason why $\gruConGame{\oneptcomp X}{\infty}$ and $\gruKPGame{X}$ are
not completely equivalent is due to the fact that $\pl P$ may hide information
from $\pl O$ by playing $\infty$. These moves cannot trivially be ignored
using a $k$-limited information strategy for $k\geq 2$, since $\pl P$ may
ensure that only one ``useful'' move may be seen by $\pl K$ at a time by playing
$k$ $\infty$'s between each non-$\infty$.

@@

\begin{defn}
  A space is \term{metacompact} if for every open cover $\mc U$ there exists a
  point-finite open refinement $\mc V$ of $\mc U$ also covering the space.
\end{defn}

@@

\begin{defn}
  A space is \term{$\sigma$-metacompact} if for every open cover $\mc U$ there
  exist point-finite open refinements $\mc V_n$ of $\mc U$ such that
  $\bigcup_{n<\omega}\mc V_n$ also covers the space.
\end{defn}

@@

A similar game may be considered by allowing the second player to choose
compact sets rather than points, which provided in \cite{MR858337}
a game-theoretic characterization of paracompactness for locally compact
spaces.

\begin{game}
  Let $\gruKLGame{X}$ denote the \term{Gruenhage compact/compact game}
  with players $\pl K$, $\pl L$. This game proceeds analogously to
  $\gruKPGame{X}$, except the second player $\pl L$ chooses compact sets $L_n$
  missing $\bigcup_{m\leq n}K_n$,
  and $\pl K$ wins if the collection $\{L_n:n<\omega\}$ is locally finite.
\end{game}

@@

\begin{defn}
  A space is \term{paracompact} if for every open cover $\mc U$ there exists a
  locally-finite open refinement $\mc V$ of $\mc U$ also covering the space.
\end{defn}

@@

\begin{defn}
  A space $X$ is \term{hemicompact} if there exist compact sets $K_n$ for
  $n<\omega$ such that every compact set in $X$ is a subset of some $K_n$.
\end{defn}

@@

\begin{proof}
  Let $\sigma$ be a winning predetermined strategy for $\pl K$ in
  $\gruKPGame{X}$. If $C\in \mc K(X)$ is compact, then for each $x\in C$ let
  $U_x$ be an open neighborhood of $x$ which intersects finitely many
  $\sigma(n)$. Choose $x_i\in C$ for $i<n<\omega$ such that
  $\{U_{x_i}:i<n\}$ covers $C$. Then $\bigcup_{i<n}U_{x_i}$ contains $C$
  and intersects finitely many $\sigma(n)$, and thus
  $\{\bigcup_{m\leq n}\sigma(m):n<\omega\}$ witnesses hemicompactness.
\end{proof}

@@

It is not possible to prove in $ZFC$ that
$\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$
for arbitrary free ultrafilters.

@@

\begin{defn}
  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct
  clopen sets, along with an uncountable subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\pmb X$ is given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $B_{\alpha,m}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
  $m<\omega$.
\end{defn}

@@

\begin{lem}
  $K_F$, $K_F'$, and $L_m$ are compact in $\pmb X$.
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lem}

@@

  Now consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
  Then if $\pmb p(n)=\<x,s\>$ with $\alpha = \alpha_{x,N}$ for some $N<\omega$,
  then $\pmb p(m)\not\in B_{\alpha,0}$ for $\max(n,N)<m<\omega$.
  Or, if $\pmb p(n)=c_\alpha$, then
  $\pmb p(m)\not\in B_{\alpha,0}$ for $n<m<\omega$.
  Otherwise, $\pmb p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
  In any case, $B_{\alpha,0}$ is a neighborhood of $\pmb x$ which contains finitely
  many $\pmb p(n)$. Therefore, $\sigma$ is a winning strategy.
\end{proof}

@@

\begin{proof}
  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
  compact; one such space was constructed in \cite{Marciszewski1991291}.
  >et $X=Y^2$.
  Then by characterizations of Corson and Eberlien compacts found in
  \cite{MR752278},
  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
  clopen cover of $X$ which is not $\sigma$-point-finite.
\end{proof}

\begin{cor}
  There exists a locally compact space $X$ such that $\pl K\win\gruKPGame{X}$
  but $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
\end{cor}

So the following questions remain open:

\begin{ques}
  Does $\pl K\ktactwin{k+1}\gruKPGame{X}$ imply
  $\pl K\tactwin\gruKPGame{X}$ for all locally compact spaces?
  Equivalently, is metacompactness characterized by
  $\pl K\ktactwin{k+1}\gruKPGame{X}$ for all locally compact spaces?
  What about for Markov strategies and $\sigma$-metacompactness?
\end{ques}
